
```{r}
library(rje)
```

# Fast but loose implementations of AND and OR logical operators.

```{r}
and0(c(0,1,0), c(1,1,0))
## Not run: 
set.seed(1234)
x = rbinom(5000, 1, 0.5)
y = rbinom(5000, 1, 0.5)

# 3 to 4 times improvement over `&`
system.time(for (i in 1:5000) and0(x,y))
system.time(for (i in 1:5000) x & y)
```
# Fast and loose application of function over list.

This is just a wrapper for unlist(lapply(x, FUN)), which will behave as sapply if FUN returns an atomic vector of length 1 each time.

Speed up over sapply is not dramatic, but can be useful in time critical code.

```{r}
x = list(1:1000)
tmp = fsapply(x, sin)

## Not run: 
x = list()
set.seed(142313)
for (i in 1:1000) x[[i]] = rnorm(100)

system.time(for (i in 1:1000) sapply(x, function(x) last(x)))
system.time(for (i in 1:1000) fsapply(x, function(x) last(x)))
```



# Get inclusion maximal subsets from a list

```{r}
letlist <- list(LETTERS[1:2], LETTERS[2:4], LETTERS[1:3], LETTERS[3:6])
inclusionMax(letlist)
```

# Compute margin of a table faster

```{r}
m <- matrix(1:4, 2)
marginTable(m, 1)
marginTable(m, 2)

propTable(m, 2)

# 3-way example
m <- array(1:8, rep(2,3))
marginTable(m, c(2,3))
marginTable(m, c(3,2))
marginTable(m, c(3,2), order=FALSE)

#' set.seed(2314)
# set of 10 2x2x2 probability distributions
x = rdirichlet(10, rep(1,8))

marginMatrix(x, c(1,3))
marginMatrix(t(x), c(1,3), incols=TRUE)
```


```{r}
x = list(1:2, 1:3)
y = list(1:4, 1:3)
setmatch(x, y)
subsetmatch(x, y)
setsetdiff(x, y)

x = list(1:3, 1:2)
y = list(2:1, c(2,1,3))
setsetequal(x, y)
```


```{r}
x=replicate(10, sample(1:5,3,T), F)

setsetdiff(list(1:3,4:5), x)
```

```{r}
subsetOrder(2:4, 1:4)
subsetOrder(2:4, 3:5)
```

```{r}
is.subset(1:2, 1:3)
is.subset(1:2, 2:3)
1:2 %subof% 1:3
1:2 %subof% 2:3
```

```{r}

```











