---
title: "How to Use 'crtcr'"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{How to Use 'crtcr'}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

# Convergent Recombination of TCR Clones

# Guide to crtcr R package

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Installation

```{r}

```

## Data transformation - clones vs. clonotype

same sequence different clone example

```{r}

```

### Data types

```{r}

```

### Get clonotype function - get_clonotype

```{r}

```

## Convergent recombination level (CR-level)

-   different ways to calculate by clone defenition
-   cr level in a repertoire
-   cr level across populations

different ways to calculate by clone defenition

```{r}

```

cr level in a repertoire

```{r}
# cr_level
```

cr level across populations

```{r}
# cr_level_matrix
```

## Clonotype sharing

- single population
  - clonotype 
  - clone
- multiple populations
  - clonotype 
  - clone

single population - clonotype

```{r}
# shared_clonotype
```

single population - clone

```{r}
# shared_clone
```

multiple populations - clonotype

```{r}
# shared_population_clonotype
```

multiple populations - clone

```{r}
# shared_population_clone
```

## Public clonotypes subtypes classification

example

- logical
  - is private
  - is public
    - is public exclusive
    - is public inclusive
- table
- factor
- list

logical

```{r}
# public_cr
```

table

```{r}
# cr_table
```

factor

```{r}
# factor_cr
```

list

```{r}
# cr_list
```


## Clonotypes overlapping

- among individuals
- among populations
- among sub-populations

```{r}
# cr_overlap
```
