---
title: "How to Use 'crtcr'"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{How to Use 'crtcr'}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

# Convergent Recombination of TCR Clones

# Guide to crtcr R package

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Installation

CRAN

```{r}
install.packages("crtcr")
```

GitHub

```{r}
# devtools::install_github("systemsbiomed/crtcr")
```

## Data transformation - clones vs. clonotype

### same sequence different clone example

differentiating by the nucleotide sequence

```{r}

```

differentiating by the the V-segments of the CDR3 amino acid sequence

```{r}

```

differentiating by multiple attributes of the CDR3 amino acid sequence like the CDR3's nucleotide sequence and also its V- and J-segment

```{r}

```

### Data types

### for cr-level functions

repertoire's clonotypes - of individual/sample - as a characrer vector - as a data frame

### for share-level functions

population's clonotypes - group of individuals with characteristic in common (such as test or control group) - as a list of characrer vectors - as a list of data frames - a data frame with id column

### for cr-type functions

multiple populations' clonotypes - multiple groups to be compared - as list of - list of character vectors - population vectors - as list of - list of data frames - population's combined data frame with id column - as a data frame with with two id columns, one for the individual and one for the group

get_clonotype

```{r}

```

get_group_clonotype

```{r}

```

get_multiple_group_clonotype

```{r}

```

## Convergent recombination level (CR-level)

the right calculation is based on how a clone is defined. use the previous function to adjust data or the 'clone_by' field

-   CR-level of a clonotype
-   CR-level across repertoire
-   CR-level in a group
-   Compare CR-level by different "clone definitions"

cr_level - this function execute the following by the of argument

cr_level_clonotype - CR-level value of a clonotype in a repertoire

```{r}
# cr_level
```

cr_level_rep - CR-level of all clonotype in a repertoire

```{r}
# cr_level_matrix
```

cr_level_group - CR-level across multiple populations' clonotypes

```{r}

```

cr_level_compare - computes CR-level for every clone definition

```{r}

```

## repertoires sharing-level

-   of a population's clonotype
-   of multiple populations' clonotype
-   sharing-level conditioned by clone's property

single population - clonotype

```{r}
# shared_clonotype
```

single population - clone

```{r}
# shared_clone
```

multiple populations - clonotype

```{r}
# shared_population_clonotype
```

multiple populations - clone

```{r}
# shared_population_clone
```

## Convergent recombination classification

## Public clonotype subtypes

[explin]

-   private and public
-   public exclusive
-   public inclusive

### CR functions:

logical operation - is private - is public - is public exclusive - is public inclusive

Data transformation - add a column - split data frame - clonotype factor - clonotype label - clonotype list

Significant values by CR-type - CR-level to CR-type - share-level to CR-type - clone count - clone frequency

Pairwise resemblance (overlapping, similarity, correlation, distance, etc.) - individual-wise - population-wise - sub-populations-wise

```{r}
# cr_overlap
```
